Capstone Movielens Report

### 2025-11-16 reports/capstone-movielens.site/05.appendix.Rmd
Fix for function description: tune.model_param.

::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
  - **steps.beyond_min:** (default 2; only takes effect if [break.if_min](func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.

##### Details
\
The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#fn_tune.test.param_value) argument.

When the minimum *RMSE* value is reached, the algorithm terminates if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.
Otherwise, the algorithm continues iterating and terminates after the number of cycles specified by the [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) argument.

>>>>

::: { #func.tune.model_param.args.steps.beyond_min .sidebar }
  - **steps.beyond_min:** (2 by default; only takes effect if [break.if_min](#func.tune.model_param.args.break.if_min) is `TRUE`) Specifies the number of steps after finding the minimum *RMSE* value after which the algorithm should terminate.

The algorithm iterates through the $\lambda$ parameter values from the list passed in the [param_values](#func.tune.model_param.args.param_values) argument, computing the model's *RMSE* for each of them, using the helper function specified by the [fn_tune.test.param_value](#func.tune.model_param.args.fn_tune.test.param_value) argument.

The algorithm continues iterating until the end of the  $\lambda$ parameter values list if [break.if_min](#func.tune.model_param.args.break.if_min) is `FALSE`.

Otherwise, the algorithm terminates after the number of cycles specified by the argument [steps.beyond_min](#func.tune.model_param.args.steps.beyond_min) has completed since the minimum *RMSE* value was reached.
